Defending Against Web Application Attacks: Approaches, Challenges and Implications \newline\newline \small{\textbf{Response to Review Comments}}

### 2016-07-19 docs/comments/comments.tex
first steps of the revision

\titlespacing*{\section}
{0pt}{1ex}{0.6ex}
\titlespacing*{\subsection}
{0pt}{1ex}{0.6ex}
\titlespacing*{\subsubsection}
{0pt}{1ex}{0.6ex}

@@

\lstset{columns=flexible,showstringspaces=false}
\lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
\lstset{aboveskip=3.5pt,belowskip=3.5pt}

@@

\title{Defending Against Web Application Attacks: Approaches, Challenges and Implications \vspace{-1mm}}

@@

\section{Introduction}

Web application attacks may involve security misconfigurations, broken
authentication and session management, or other issues. Some of the
most dangerous and prevalent web application attacks, however,
exploit vulnerabilities associated with improper validation or filtering
of untrusted inputs, resulting in the injection of malicious
script or domain-specific language code.
Attacks of this type include Cross-Site Scripting ({\sc xss})~\cite{SG07},
and {\sc sql} injection attacks~\cite{RL12b},
%and Cross-Site Request Forgery
% ({\sc csrf}) attacks~\cite{LZRL09},
among others.

For the past several years,
these attacks have been topping the lists of the most dangerous vulnerabilities
published by
{\sc owasp},\footnote{\scriptsize\url{https://www.owasp.org/index.php/Top_10_2013-Top_10}}
%~\cite{OWASPtop10},
{\sc mitre},\footnote{\scriptsize\url{http://cwe.mitre.org/top25/}}
%~\cite{MITREtop25},
and other organizations.
For instance, consider the case of {\sc owasp}'s popular Top Ten
project,%\footnote{\url{https://www.owasp.org/index.php/Top_10_2013-Top_10}}
%~\cite{OWASPtop10},
which aims to raise awareness about web application security by
identifying some of the most critical risks organizations may face.
In its three consecutive Top Ten lists (2007, 2010, 2013), different
injection attacks dominate the top five positions.

At the same time, attackers find new ways~\cite{HNSHS12,DKH14}
to bypass defense mechanisms using a variety of techniques,
despite the numerous countermeasures that are being introduced.
As an example, already by 2006,
there were more than 20 proposed defenses
against {\sc sql} injection attacks~\cite{HVO06}.
Since then, the number has doubled, while researchers have indicated that
the number of {\sc sql} injection attacks has been steadily
increasing in recent years~\cite{SSL12}.

In this paper, we explore how different attacks associated with 
the exploitation of untrusted input validation errors can be modeled 
under a {\it common perspective}. To that end, we propose an exploitation
model which highlights that most of the steps needed to mount
different types of code injection attacks are
common.\footnote{\scriptsize Note that we do not consider lower-level attacks based on
the exploitation of memory corruption vulnerabilities and the injection
of binary code---see Section~\ref{sec:attacks}.} This is validated by the fact that
some protection mechanisms defend against more than one of these
types of attacks.

Then, we {\it categorize} a selection of representative
protection mechanisms. In our selection we include protection
mechanisms that counter web attacks when they take place,
while we do not consider countermeasures that identify
vulnerabilities using static program analysis~\cite{SZ12}
(which takes place during the development or testing
phases). Similarly, dynamic analysis techniques that examine
applications to identify vulnerabilities that may lead to the attacks
that we described earlier are out of scope as well. Note also, that we
didn't consider mechanisms that haven't been presented in research papers.

Furthermore, we {\it analyze} each mechanism across the
following dimensions:
\begin{itemize}
\item {\it Accuracy:} protection mechanisms are as good
  as their detection capability; this requires low false positive and
  false negative rates.
\item {\it Availability:} whether the protection mechanism and its
  testbed are publicly available.
\item {\it Performance overhead:} the 
  overhead imposed by the mechanisms at their points of deployment.
\item {\it Ease of use:} whether the
  mechanism is practical in terms of deployment
  and can be easily adopted by security experts.
\item {\it Security:} the robustness of the protection mechanism against
  attackers with knowledge of its internals who attempt to circumvent it.
\item {\it Detection Point:} the location where a mechanism detects an attack
  based on our exploitation model.
\end{itemize}
\noindent
All the above requirements are considered important
when building mechanisms for the protection of
applications~\cite{A01,A00,SPWS13,nature2014}.
Based on this analysis, we identify the advantages
and disadvantages of the
various mechanisms and enumerate some of their common
characteristics. We also draw useful conclusions
about the various protection categories and see how they compare
to each other.
In addition, we attempt to shed light on the factors
that may impede the adoption of defenses in practice.
Finally,
we provide some lessons and recommendations that
developers of new defenses may find helpful.

The main contributions of this paper are the following:

\begin{enumerate}
\item We provide a unified exploitation model for different types of
  web application attacks based on code injection.
\item We categorize and analyze proposed defenses using a set of
  criteria that are important for building protection mechanisms.
\item We provide insight based on the issues that arise from our analysis.
  We put emphasis on factors that may hinder the widespread deployment of
  protection mechanisms, and the transition of tools from research to practice.
\end{enumerate}
\vspace{-0.05mm}

The rest of the paper is organized as follows:
Section~\ref{sec:attacks} provides some insights on
web code injection attacks and
Section~\ref{sec:model} presents our proposed model.
Section~\ref{sec:dimensions} introduces the dimensions
across which we analyze the various defenses.
Our categorization and analysis is presented in
Section~\ref{sec:defs} and our observations are
provided in Section~\ref{sec:discussion}.
Finally, Section~\ref{sec:lessons-learned}
highlights some lessons learned from our observations
and Section~\ref{sec:conclusion} concludes the paper.

\section{Code Injection Attacks in Web Applications}
\label{sec:attacks}

Lack of input validation is a major vulnerability behind dangerous web
application attacks. By taking advantage of this, attackers can inject
their code into applications to perform malicious tasks. Exploits of
this kind can have different forms depending on the execution context
of the application and the location of the programming flaw that leads
to the attack.

Bratus et al.~\cite{BLSPS11} portray the issue in a more generic way:
{\it ``unexpected (and unexpectedly powerful) computational models
  inside targeted systems, which turn a part of the target into a
  so-called `weird machine' programmable by the attacker via crafted
  inputs (a.k.a. `exploits').''} In particular, {\it ``every
  application that copies untrusted input verbatim into an output
  program is vulnerable to code injection.''} Ray and
Ligatti~\cite{RL12b} have proved this claim based on formal language
theory.

\begin{figure}
\begin{center}
\leavevmode
\includegraphics[scale=0.55]{attack-tree-uml.pdf}
\end{center}
\vspace{-5mm}
\caption{\label{fig:taxonomy}A taxonomy of dynamic and domain-specific
language code injection attacks against web applications.}
\vspace{-5mm}
\end{figure}

Code injection attacks can be divided in two categories. The first
involves binary code and the second higher-level language code. An
extensive survey on binary code injection attacks was conducted by
Lhee and Chapin~\cite{LC03}. Advances in memory corruption vulnerability
exploitation have been studied extensively~\cite{PB04, SPWS13}
and countermeasures to such attacks
have already been analyzed~\cite{YJP12}.
% \cite[Sec. 13.8]{DKZ12}.
In this work we do not consider binary code injection,
focusing instead on defenses
that protect web applications against attacks based on the
injection of higher-level language code.

Figure~\ref{fig:taxonomy} presents a taxonomy of source
code injection attacks against web applications.
Such attacks may involve high-level language code, written in either a
{\it Domain Specific Language} ({\sc dsl}) or a {\it Dynamic Language}.
To illustrate, we discuss examples from both categories
that will be used throughout the paper.

Injection attacks that involve {\sc dsl}s constitute an important
subset of the code injection problem, as {\sc dsl}s such as
{\sc sql} and {\sc xml} play a significant role in the development of
both web and mobile applications. For example, many applications have
interfaces through which a user enters input to interact with the
application, thereby interacting with the underlying database. This
input can become part of an {\sc sql} query and gets executed on the
target database. Code injection attacks that exploit vulnerabilities
in database interfaces by taking advantage of input validation issues,
such as incorrectly passed parameters or incorrect type handling, are
called {\sc sql} injection attacks~\cite{MS09,HVO06,SW06}.
Consider a trivial exploit that takes advantage of incorrectly
filtered quotation characters in an application that shows the
password of a forgetful user by executing the following
query:

\lstset{language=SQL}
\begin{lstlisting}
SELECT password from userdata WHERE id = 'Alice'
\end{lstlisting}

\noindent
Attackers that would input the string {\tt anything' OR 'x'='x}
could view every item in the table.
%obtain a user's password by email.
Savvy programmers can use certain {\sc api} functions, such as {\sc php}'s
{\tt mysql\_real\_escape\_string()}, to detect malformed input, or,
better, use prepared {\sc sql} statements instead of statement
templates. Unfortunately, the increasing number of {\sc sql} injection
attacks suggests that programmers are not always that careful. Using
similar techniques, malicious users can mount other exploits based on
{\sc dsl}s such as {\sc xp}ath~\cite{SW06,CDL07}, {\sc
  xml}~\cite{MSM13} and {\sc json}~\cite{SMS13}. The effects can be
wide-ranging. A malicious user can view sensitive information, destroy
or modify protected data, or even crash the entire application.

{\sc html} is another {\sc dsl} that can be used for malicious
purposes when an application does not properly handle user-supplied
data. Based on this vulnerability attackers can supply valid {\sc
  html}, typically via a parameter value, and inject their own content
into the application's page. {\sc html} injection is mainly associated
with {\sc xss} attacks~\cite{SP11, SLMS14}. However, {\sc html} injection
can also be used as a vehicle for Cross-Site Request Forgery
({\sc csrf}) attacks~\cite{BJM08, LZRL09}
(even though a common {\sc csrf} attack does not necessarily
involve code injection).
Consider a bulletin board system where {\tt img} tags are allowed.
A malicious user could embed a {\sc csrf} request within an
{\tt img} tag in the following manner:

\lstset{language=HTML}
\begin{lstlisting}
<img src='http://www.vulnerable.com/admin.php?edituserwithID=13&addgroup=admin'/>
\end{lstlisting}

\noindent
When the page with this injected code is accessed by an administrator,
the attacker (with {\sc id} 13) will gain administrative privileges
over the vulnerable.com web page,
while the administrator of the bulletin board system
will have no immediate indication that there has been an attack.

A recent class of code injection attacks involve dynamic languages
such as JavaScript and {\sc php}~\cite{SFVM09,SMS13}.
JavaScript injection attacks make up a large subset of dynamic
language code injection attacks and are considered a critical issue
in web application security mainly because they are associated with
major vulnerabilities such as {\sc xss} attacks~\cite{SG07} and
Cross-Channel Scripting ({\sc xcs}) attacks~\cite{W10,BBB09}.
Such attacks are enabled when a web application accepts
and redisplays data of uncertain origin without
proper validation and filtering. Based on this flaw, an attacker
can manage to inject a script in the JavaScript engine of a browser
and alter its execution flow~\cite{ELX07}.
For a typical {\sc xss} example that involves JavaScript injection
consider a web page that prints the value
of a query parameter ({\tt query}) from the
page's {\sc url} as part of the page's content
without escaping the value. Attackers
can take advantage of this and inject an {\tt iframe} tag
into the page to steal a user's cookie and
send it via an image request to a web site
under their control (malicious.com).
This could be achieved by including the following
link to the malicious web site (or sending it via phishing
email) and inducing the user to click on it:

\lstset{language=HTML}
\begin{lstlisting}
http://example.com/vulnerable.html?query=<iframe src="javascript:document.body.innerHTML=+'<img src=\"http://malicious.com/?c='+encodeURIComponent(document.cookie)+'\">'"></iframe>
\end{lstlisting}

\noindent
Note that in many cases {\sc xss} attacks
involve the injection of both {\sc html} and JavaScript code.

A simple example of a {\sc php} injection attack is an input string
that is fed into an {\tt eval()} function call, e.g.:

\lstset{language=PHP}
\begin{lstlisting}
$variable = $_GET['var']; 
$input = $_GET['value'];
eval('$variable = ' . $input . ';')
\end{lstlisting}

\noindent
The user may pass into the {\tt value} parameter code that will
be executed on the server. Hence, if an attacker provides as
input the following string: {\tt 10 ; system("touch foo");}
then a file will be created on the server---it is easy
to imagine more detrimental scenarios.

A recent attack called {\sc php} Object Injection
({\sc poi})~\cite{DKH14} does not directly involve
the injection of code, but still achieves arbitrary code execution
in the context of a {\sc php} application through the
injection of specially crafted objects.
These objects are injected as part of cookies,
which, when deserialized
by the application, result in arbitrary code execution.
Note that the exploitation model we propose
in the following Section also captures such attacks.

\begin{figure*}[t]
\begin{center}
\leavevmode
\includegraphics[scale=0.48]{attacks-steps-CSRF.pdf}
\end{center}
\vspace{-5.5mm}
\caption{\label{fig:attacks}Attack model for dynamic and domain specific
language code injection in web applications.
Transitions are labeled with the different attacks that use that path,
while the numbers next to attack labels denote the 
sequence of steps for a particular attack.
Points where different types of defenses
detect or prevent attacks are marked with an `X' symbol:
(1) {\sc ub} (at the browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,VFJKKV07,SLMS14,BV08,SSM10},
(2) {\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,GC09,JB07,NLC07,WPLKK09,JEP08,PS11},
(3) {\sc dbal} (at the database abstraction layer):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05b,SMS13},
(4) {\sc db} (at the database):~\cite{BK04,LLW02,VMV05}.}
\vspace{-6mm}
\end{figure*}

\section{Exploitation Model}
\label{sec:model}

We provide a step-by-step exploitation model to aid in understanding the process
of carrying out code injection attacks against web
applications. Figure~\ref{fig:attacks} illustrates the required steps for
different classes of attacks,
such as {\sc sql} injection, {\sc xss}, and {\sc csrf}. Links between steps are
labeled with the different attacks that use that path, while the
numbers next to attack labels denote the sequence of steps for a
particular attack. Most steps are common in all attacks, as different attack
types follow similar exploitation paths, as mentioned in
the previous section. Large `X' marks on transitions correspond to the
points where the defenses we consider in this work detect or prevent attacks.

An attacker can initiate an injection attack through two main routes.
One way is to use the browser of a victim as an attack
vehicle, through which the code will be injected in the application.
For example, the attacker could embed a malicious script into a {\sc
  url} and then trick a user to click on it through social
engineering, e.g., by sending a phishing email (transition {\sc p-xss} 1.1, {\sc
  n-xss} 1.1, {\sc csrf} 1). Alternatively, the attacker may be able
to inject directly the malicious code on the server through an {\sc http} request
({\sc dsl} 1, {\sc p-xss} 1, {\sc n-xss} 1, {\sc i-csrf} 1). This would happen
in a web application that accepts and processes user input
without appropriate validation. An attacker could upload data
containing a specially crafted script
to steal the cookies of the visiting users ({\sc p-xss} 1, {\sc n-xss} 1),
an {\tt img} tag including a malicious {\sc http} request ({\sc csrf 1}, {\sc
i-csrf 1}),
or embed malicious
{\sc sql} code to retrieve private data from a database ({\sc dsl} 1).
Note that, {\sc xss} and {\sc csrf} attacks can start from both routes.
Once the injected code reaches the vulnerable application, it becomes
a part of a value represented by a program variable. The target of the
attack determines the route from that point and on. In an {\sc sql} injection
attack, the injected code becomes part of a query that
eventually reaches the database where it is executed.

Cross-site scripting attacks fall into two categories, {\it non-persistent}
(also known as \emph{reflected}) {\sc xss}
and {\it persistent} (also known as \emph{stored}) {\sc xss}.
Non-persistent {\sc xss} attacks take place when the
data provided by a user is processed on-the-fly
by server-side application logic and ends up without proper sanitization
into a dynamically generated response ({\sc p-xss} 7, {\sc n-xss} 2)
that is eventually rendered by the user's browser.
Thus, in a non-persistent {\sc xss} attack, the injected code
is not saved on the server, but immediately becomes part of the
content that is sent back to a user.
In persistent {\sc xss} attacks, on the other hand,
malicious code is permanently stored on the server ({\sc p-xss} 5).
The injected code residing at server-side then re-enters the
application's execution flow and becomes part of the content that is
eventually sent to the user as part of a future response.

{\sc csrf} attacks typically involve just a
{\sc url} or page that contains a malicious request towards
a site vulnerable to {\sc csrf}.
An attacker can entice a victim to click on the {\sc url} or visit the page
through social engineering ({\sc csrf} 1), which will the result in a malicious
request towards the vulnerable site ({\sc csrf} 2).
Note that this scenario does not involve the injection of any code through the
exploitation of some server-side vulnerability (as is the case with Server 1).
On the other hand, {\sc csrf} is also possible through injection
({\sc i-csrf}---recall our example in the previous section).
In this attack, an attacker
manages to inject {\sc html} code that contains
a malicious {\sc csrf} request in the way we described in
Section~\ref{sec:attacks}.
This code will be stored
in the database ({\sc i-csrf} 5)
and then it will re-enter the application when
a user visits a page ({\sc i-csrf} 6). When the
content reaches the browser, a malicious request will be generated
towards the site that is vulnerable to {\sc csrf}.

\section{Analysis Dimensions}
\label{sec:dimensions}

Research on web application attack defense mechanisms has a dual
character. First, a defense mechanism may be important, and therefore
publishable, because it shows that an attack can be detected or prevented in a
reliable manner. Second, a defense mechanism may be important not
just as a research contribution, but as a practical tool, if it can be
used by administrators and users to shield their applications
against the supported attacks.

The detection and prevention of attacks
in a reliable manner can be analyzed using
criteria common with other research fields:
\begin{itemize}
\item Statistical measurements that show how
reliable the detection really is.
\item Research practices that promote replication and validation
of the findings.
\end{itemize}

\noindent
Whether a reliable defense mechanism has value in a practical
setting rests on a different set of criteria:
\begin{itemize}
\item What are the overheads imposed by the mechanism?
\item How easy is it to deploy and use the mechanism?
\item How robust is it against ways to circumvent it?
\item At which point throughout the system does it block an attack?
\end{itemize}

The first two criteria correspond to \emph{Accuracy} and
\emph{Availability}. The other four criteria correspond to \emph{Runtime
  Performance}, \emph{Ease of Use}, \emph{Security}, and
\emph{Point of Detection}.

\subsection{Accuracy}
\label{ssec:diagnostic-performance}

Web application defenses 
crucially have to capture the presence of an attack. This, however, does not
make a defense mechanism immediately useful. A
detection mechanism must also be reliable.
Detection accuracy is gauged with the following
metrics~\cite{GFDLS06,A00}:
\begin{itemize}
\item {\bf Sensitivity}: the probability that an attack will be
  caught.
\item {\bf Specificity}: the probability that a normal interaction
  will not be flagged.
\item {\bf Positive Predictive Value} ({\sc ppv}): the probability that a
  reported attack is a real attack. It is the conditional probability
  that an event is an attack if the detection mechanism flags it as
  such. 
\item {\bf Negative Predictive Value} ({\sc npv}): the probability that if
  nothing is reported, no attack has taken place. It is the conditional
  probability that an event is not an attack given that the detection
  mechanism flags it as normal.
\end{itemize}

\noindent
We will focus on sensitivity and specificity; we will come back to
\textsc{ppv} and \textsc{npv} in Section~\ref{sec:lessons-learned}.
Sensitivity and specifity are defined as follows~\cite{linn2004}:
\begin{itemize}
\item True Positive (\textsc{tp}): an attack that raises an alarm.
\item True Negative (\textsc{tn}): an event that is not an attack and that does
  not raise an alarm.
\item False Positive (\textsc{fp}): an event that although it is not an attack,
  raises an alarm.
\item False Negative (\textsc{fn}): an event that although is an attack, does
  not raise an alarm.
\end{itemize}

\noindent
With these we can calculate:

\vspace{0.5mm}
\noindent\begin{minipage}{0.5\linewidth}
\begin{equation}
  \textsc{se} = \textrm{Sensitivity} = \frac{\textsc{tp}}{\textsc{tp}
    + \textsc{fn}}
\label{eq:sensitivity}
\end{equation}
\end{minipage}%
\begin{minipage}{0.5\linewidth}
\begin{equation}
  \textsc{sp} = \textrm{Specificity} = \frac{\textsc{tn}}{\textsc{fp}
    + \textsc{tn}}
\label{eq:specificity}
\end{equation}
\end{minipage}\par\vspace{\belowdisplayskip}

\noindent
Sensitivity and specificity can be calculated based on test
data alone. To calculate sensitivity, we run the test on a
controlled environment where we allow only attack events to reach the
system. The ratio of reported attacks over all attacks will give us
the sensitivity. Similarly, to calculate the specificity we can run
the test on a controlled environment where we allow only innocuous
events to reach the system. The ratio of non-reported events over all
events will give us the specificity.
Note that the use of sensitivity and specificity in this context
has been advocated before~\cite{PP12}.

\subsection{Availability}

To ensure reproducibility of research results, the source code
implementing a detection mechanism should be available to researchers.
Ideally the code should be available under an open source license, so
that it is easy to modify and improve an approach; even when this is
not possible, for whatever reason, it is important to make sure that
all computer code and test data is available, noting any restrictions
on accessibility. Availability of computer code has been recognized as
an important issue outside the computer science field: the journal
\emph{Nature}, in a recent editorial, adopted a publication policy stressing
access to code and data~\cite{nature2014}. At a time and date that the
merits of open access to code are discussed in non computer science
journals~\cite{easterbrook2014}, we should expect computer scientists
to lead the way.

\subsection{Performance Overhead}

Detection mechanisms may impose a cost due to their use, as they
typically introduce some amount of extra computation on existing applications.
The overhead depends on the specifics of each mechanism. For
example, it may be due to some form of run-time checking, or some form of
obfuscation. Also, depending on the approach, the cost may be incurred
on different places: it may affect a server
(e.g., its memory or {\sc cpu} usage, processing throughput, or response latency),
it may affect the client, or both. The
usefulness of a mechanism depends therefore on the
computational cost it requires and on where it imposes it, as
different overheads may be acceptable at the server-side than the client-side.
What kind of numbers is reported matters as well. Reporting absolute
measurements gives little information on the actual overhead, unless
separate measurements are given for the system under study with and
without the proposed mechanism. Percentage measurements are normally
better.

Performance evaluation rests on strong foundations~\cite{jain1991} and
is a vibrant field as new technologies emerge~\cite{gregg2014}.
Although it may not be necessary to conduct a comprehensive
performance evaluation analysis for a defense mechanism, the more
evaluation results are provided for a mechanism, the more valuable
it becomes as a practical approach.

\subsection{Ease of Use}
\label{sec:deployment}

The value of a detection mechanism as a practical tool depends on how
easy it is to deploy it in a production setting. This aspect is
orthogonal to the
value of a detection mechanism as a research finding. Devising a
technique to detect a hitherto undetectable class of attacks may be an
excellent research contribution that merits publication; it may also
be heavily cited and open the road to other, practical
implementations in the future.

Ease of use depends on the deployment process required for the
mechanism. The detection mechanism may be deployed at either or both
the server and the client-side. Deployments on just the server or the client are
easier to handle than deployments on both of them. The mechanism may
be an add-on or plugin for existing software, client or server, or it
may be tightly integrated with existing software, requiring rebuilding
from source code.

No matter where it is installed, the means of installation influences
ease of use. A detection mechanism that is available as a ready-to-install
package will trump others that only exist in the form
of source code.

\subsection{Security}

Defenders and attackers are often caught in a cat-and-mouse game,
where countermeasures are bypassed by canny attacks, which are caught
by more sophisticated countermeasures, yet again bypassed by cannier
attacks, and so on. We use security to refer to the ability of a
detection mechanism to resist circumvention.

A mechanism that has not been bypassed is not eternally secure, as it
is possible that a bypass method will be discovered in the future. We
examine the various approaches based on the knowledge we have so far,
that is, whether there are any known ways to bypass the detection
mechanism today.

\subsection{Point of Detection}
\label{sec:point}

Detection mechanisms vary on the location where they detect an attack.
There are four different points where an attack can be caught, as seen
in Figure~\ref{fig:attacks}:

\begin{enumerate}
\item At the user's browser (Point {\sc ub}).
\item En route from the server to the user's browser---in most cases
within a proxy (Point {\sc s}t{\sc b}).
\item At the database abstraction layer, before it reaches the server's database
  (Point {\sc dbal}).
\item After the malicious code reaches the server's database
  (Point {\sc db}).
\end{enumerate}

\begin{figure}[t]
\begin{center}
\leavevmode
\includegraphics[scale=0.54]{defenses.pdf}
\end{center}
\vspace{-5.4mm}
\caption{\label{fig:defenses}The basic categories of countermeasures
against web application attacks based on code
injection. For each approach we provide the references
that present corresponding mechanisms:
{\it Policy Enforcement}:~\cite{NSS06,JKK06a,KJKV09,TNH07,RDWDE07,YCIS07,OWVS08,PSC09,ML10,DDHPJ10,PS11,VDDPJ11,BV08,SSM10},
{\sc isr}:~\cite{BK04,JB07,GC09,APKLM10},
{\it Parse-Tree Validation}:~\cite{BWS05,SW06},
{\it Taint Tracking}:~\cite{HCF05,PB05,XBS06,NLC07,VFJKKV07,PMP11,SLMS14},
{\it Training}:~\cite{LLW02,HO05b,VMV05,JEP08,WPLKK09,MS09,MKLS11},
{\it Hybrid}:~\cite{BV08,LV09,SMS13}.}
\vspace{-5.6mm}
\end{figure}

\begin{table*}[t]
  \renewcommand{\baselinestretch}{1.12}
    \caption{Comparison summary of mechanisms developed to counter application attacks based on code injection.}
    \label{tab:comp}
    \vspace{-4mm}
\centering
    \begin{threeparttable}
    \begin{small}
\scalebox{0.77}{
    \begin{tabular}{l|c|c|cc|c}
    \thickhline
    \bf{Approach}
  & \bf{Mechanism}
  & \bf{\# of Citations}
  & \multicolumn{2}{c|}{Requirements\tnote{1}}
  & \bf{Attack}\tnote{4} \\
  &&& \bf{TP,TN,FP,FN}\tnote{2}
  & \bf{Performance Overhead}\tnote{3} & \\
    \thickhline
  \multirow{2}{*}{Parse-Tree Validation}
  &   {\sc sqlg}uard~\cite{BWS05} & 305 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% ({\sc s}) & {\sc sql}i \\
  &   {\sc sqlc}heck~\cite{SW06} & 473 & (36848,7648,0,0)\_r & 3ms per query ({\sc s}) & {\sc sql}i \\
  \hline
  \multirow{13}{*}{Policy Enforcement}
  &   {\sc dsi}~\cite{NSS06} & 168 & (5268,{\sc nq},{\sc nq},85)\_r & 1.85\% ({\sc c}) & {\sc xss} \\ 
  &   NoForge~\cite{JKK06a} & 151 & (7,{\sc nq},{\sc nq},0)\_r & {\sc na} ({\sc s}) & {\sc csrf} \\
  &   Noxes~\cite{KJKV09} & 58 & (3,{\sc na},{\sc na},0)\_r & {\sc na} ({\sc c}) & {\sc xss} \\
  % &   {\it {\sc met}}~\cite{ELX07} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc xss} \\ 
  &   {\sc beep}~\cite{TNH07} & 335 & (61,{\sc na},{\sc na},0)\_r & 14.4\% ({\sc c}) & {\sc xss} \\
  &   BrowserShield~\cite{RDWDE07} & 263 & (19,{\sc nq},0,0,)\_r & 8\% ({\sc s}) & {\sc xss} \\ 
  &   CoreScript~\cite{YCIS07} & 199 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} ({\sc c}) & {\sc xss} \\
  &   {\it {\sc soma}}~\cite{OWVS08} & 56 & (5,{\sc na},{\sc na},0)\_s & 5.58\% ({\sc c}) & {\sc xss}, {\sc csrf} \\
  % &   {\it Barth et al.}~\cite{BJM08} & 271 & & {\bf ?} & {\sc csrf} \\
  &   Phung et al.~\cite{PSC09} & 101 & (37,{\sc na},{\sc na},4)\_r & 5.37\% ({\sc c}) & {\sc xss} \\
  &   ConScript~\cite{ML10} & 152 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 7\% ({\sc c}) & {\sc xss} \\
  &   CsFire~\cite{DDHPJ10} & 46 & (419582,1141807,0,3)\_r\tnote{5} & {\sc na} ({\sc c}) & {\sc csrf} \\
  &   {\sc csp}~\cite{SSM10} & 117 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} ({\sc c}) & {\sc xss}, {\sc csrf} \\
  &   j{\sc csrf}~\cite{PS11} & 4 & (2,{\sc na},{\sc na},0)\_r & 2ms ({\sc s}) & {\sc csrf} \\
  &   WebJail~\cite{VDDPJ11} & 45 & (2,{\sc na},{\sc na},1)\_{\bf ?} & $\sim$6.89ms ({\sc c}) & {\sc xss} \\
  % &   {\it TreeHouse}~\cite{IW12} & 18 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 757–-1218ms & {\sc xss} \\
  % &   {\it {\sc js}and}~\cite{AVBPDP12} & 22 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & up to 31.2\% & {\sc xss}\\
  % \hline
  % \hline 
  % \multirow{3}{*}{Securing Mashups}
  % &   {\it {\sc om}ash}~\cite{CHC08} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} & {\sc csrf} \\
  % &   {\it Mashup{\sc os}}~\cite{WFHJ07} & 149 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 1--59\% & {\sc xss} \\
  \hline
  \multirow{4}{*}{{\sc isr}}
  &   {\sc sql}rand~\cite{BK04} & 365 & (3,{\sc na},{\sc na},0)\_a & $\le$6.5{\it ms} ({\sc s}) & {\sc sql}i \\
  &   {\sc sm}ask~\cite{JB07} & 28 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} ({\sc s}) & {\sc sql}i, {\sc xss} \\
  &   Noncespaces~\cite{GC09} & 132 & (6,{\sc na},{\sc na},0)\_r &  2\% ({\sc s}) & {\sc xss} \\ 
  &   x{\sc js}~\cite{APKLM10} & 20 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40{\it ms} ({\sc c}) & {\sc xss} \\
  \thickhline
  \thickhline
  \multirow{7}{*}{Taint Tracking}
  &   Haldar et al.~\cite{HCF05} & 208 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} ({\sc s}) & {\sc sql}i, {\sc xss} \\ 
  &   {\sc csse}~\cite{PB05} & 347 & (7,{\sc nq},{\sc nq},{\sc nq})\_r & 2--10\% ({\sc s}) & {\sc sql}i, {\sc xp}athi, {\sc xss} \\
  % &   {\it SecuriFly}~\cite{MLL05} & 31 & \xmark,\tick & 9--125\% & {\sc sql} injection, {\sc xss} \\ 
  &   Xu et al.~\cite{XBS06} & 346 & (9,{\sc nq},0,{\sc nq})\_r & average 76\% ({\sc s}) & {\sc sql}i, {\sc xss} \\ 
  &   {\sc wasc}~\cite{NLC07} & 32 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 30\% ({\sc s}) & {\sc sql}i, {\sc xss} \\
  &   Vogt et al.~\cite{VFJKKV07} & 400 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_r & {\sc nq} ({\sc c}) & {\sc xss} \\
  &   {\sc php} Aspis~\cite{PMP11} & 20 & (12,{\sc nq},{\sc nq},2)\_r & 2.2$\times$ ({\sc s}) & {\sc sql}i and {\sc php}i, {\sc xss} \\
  &   Stock et al.~\cite{SLMS14} & 15 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% ({\sc c}) & {\sc dom}-based {\sc xss} \\
  \hline 

>>>>

\titlespacing*{\section}
{0pt}{1ex}{0.55ex}
\titlespacing*{\subsection}
{0pt}{1ex}{0.55ex}
\titlespacing*{\subsubsection}
{0pt}{1ex}{0.55ex}

@@

\lstset{columns=flexible,showstringspaces=false}
\lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
\lstset{aboveskip=3.3pt,belowskip=3.3pt}

@@

\title{Defending Against Web Application Attacks: Approaches, Challenges and Implications
\newline\newline
\small{\textbf{Response to Review Comments}}}

@@

\section{General Remarks}
\label{sec:rem}

We are thankful to the reviewers for their thorough reviews.
We have revised our research paper based on their suggestions and comments.
All additions and changes are highlighted in yellow
in the revised manuscript.
Number wise answers to their specific
comments / suggestions / queries are as follows.

\section{AE Comments}
\label{sec:ae}

{\bf Comment} ``Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.".\\

\noindent
{\bf Response:}
Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum".\\

\section{Reviewer \#1}
\label{sec:r1}

{\bf Comment 1:} ``Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum".\\

\noindent
{\bf Response:}
Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum".\\

\noindent
{\bf Comment 2:} ``Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum".\\

\noindent
{\bf Response:}
Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum".\\

\bibliographystyle{IEEEtran}
\bibliography{comments}
